---
title: "my-vignette"
output: rmarkdown::html_vignette
author: "haoyu ren"
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
```

Work have done

# Basic package typo/bug fix
  added parameters and corresponding documentations for functions:
      For examples:
      Added  #' @param formula object of formula
```{r}      
#' @param data dataset
#' @param n sample size
#' @param B bootstrap size
#' @param cpu number of cpu for function lm_each_subsample

#' compute the regression estimates for a blb dataset
#' @param formula object of formula
#' @param data a data set
#' @param n overall sample size for function lm_each_boot
```
Added import codes to library needed packages:
	For examples:
	Added
```{r}	
#' @import parallel
#' @importFrom utils capture.output
#' @importFrom utils read.csv
```

# Promotions
	Added parameter “CPU” as cluster input , users are able to choose the number of CPUs they want to be operated.
		For examples:

```{r,eval=FALSE}
lm_each_subsample <- function(formula, data, n, B, cpu) {
# add parallel
cl <- makeCluster(cpu)
#replicate(B, lm_each_boot(formula, data, n), simplify = FALSE)
clusterExport(cl, c("lm_each_boot", "lm1", "data"))
result <- parLapply(cl, 1:B, function(x){
  lm_each_boot(formula, data, nrow(data))
})
stopCluster(cl)
return(result)
```
	
	Added map & if statement to realize that users are able to specify a list of file of datasets rather than loading the whole dataset. If the users put a list of files to be read as parameter, it will automatically contain the data sets into a list.
For examples:
```{r,eval=FALSE}
		 if (is.data.frame(data)){
 	 data_list <- split_data(data, m)
 } else {
    		data_list <- map(data, function(x) read.csv(x))
 }
```
Added a test. Testing whether the output belongs to class “blblm”
[check() won’t pass after adding this test, the single test() works good, i didn’t solve this problem so I didn’t put the test in the package]
```{r,eval = FALSE}
	test_that("multiplication works", {
model_fit <- blblm(speed~dist, data = cars, B=100)
expect_equal(class(model_fit), "blblm")
})
```